\section{Further remarks}
\label{sec:further}

I end this note by introducing other works relevant to modular forms on $G_2$, which I don't have enough space (and knowledge) to write down the details.

\begin{itemize}
    \item We have a theory of (standard) $L$-functions for $G_2$ modular forms, especially their Rankin--Selberg type integral representations, developed by Gurevich--Segal \cite{gurevich2015rankin} and \c{C}i\c{c}ek et. al. \cite{cicek2022completed}.
    Especially, we have functional equations and Dirichlet series representations.
    \item There's an analogue of half-integral weight modular forms for $G_2$ by Leslie and Pollack \cite{leslie2024modular}, as automorphic forms on the double cover of $G_2$.
    Especially, they construct a modular form of weight $\frac{1}{2}$ on $G_2$, whose Fourier coefficients measure the size of 2-torsions of the narrow class groups.
    \item There are four other exceptional groups $F_4, E_6, E_7, E_8$, and we can define the notion of modular forms on these groups, too.
    In fact, there is a more uniform way to treat all five exceptional groups at once, via Jordan algebra and Freudenthal construction.
    This is well explained in an aribitrary paper of Pollack, e.g. \cite{pollack2020fourier}.
    \item Somehow, reductive groups of type $D_4$ also behave like exceptional groups.
    Weissman developed a similar theory of $D_4$ modular forms (to be precise, modular forms on $\Spin(4, 4)$ and $\Spin(8)$), including Fourier coefficients, local representation theory, and exceptional theta correspondences \cite{weissman2006d}.
    Interestingly, the Fourier coefficients of the $D_4$ modular forms are parameterized via Bhargava's cube \cite{bhargava2004higherI}.
    \item
    Gross and Lucianovic \cite{lucianovic2003quaternion,gross1996quaternionic} proved that there is a one-to-one correspondence between the space of \emph{ternary quadratic forms} and the \emph{quaternion algebras}, hence Fourier coefficients of genus 3 Siegel modular forms are parametrized by quaternion algebras.
    One of the main example comes from Kim's exceptional Eisenstein series on $E_7$ \cite{kim1992exceptional}, whose restriction on the Siegel upper half plane gives a weight 4 Siegel modular form with Fourier coefficients counding the number of embeddings of quaternion algebras into the Coxeter's order inside the non-split octonion.
    The \emph{anisotropic/compact} $G_2^a$ form a reductive dual pair with $\GSp_{6}$ in $E_8$,  and Volpato \cite{volpato2008some} proved that the lift of the constant function on $G_2^a$ coincides with the Siegel modular form mentioned above.
    
\end{itemize}
