\section{Introduction}
\label{sec:intro}

One of the fundamental goal of the representation theory is to classify all the irreducible representations of a given group.
In this seminar, \sout{we are} I am interested in the representations of $p$-adic groups, such as $\SL_{n}(\mathbb{Q}_{p})$ or $\Sp_{2n}(\bQ_p)$.
As in the finite group case, usual way to construct representations is by (parabolic, compact, ...) induction.
From this viewpoint, it is natural to ask what are the ``building blocks'' of irreducible representations that might exhaust all the irreducible representations by inducting them.
The answer will be \emph{supercuspidal representations}.

\begin{definition}
An irreducible admissible representation $(\pi, V)$ of $G(F)$ is called \emph{supercuspidal} if every Jacquet module $V_N := V / \langle \pi(n) v - v: n \in N, v \in V\rangle$ for parabolic $P = MN \subset G$ is zero.
Equivalently, their matix coefficients are compactly supported modulo the center.
\end{definition}


Supercuspidal representations are building blocks in the following sense:
\begin{theorem}[Bernstein {\cite{bernstein1984centre}}]
Let $(\pi, V)$ be an irreducible smooth representation of $G$.
Then there exists a parabolic subgroup $P \subseteq G$ with Levi subgroup $M$ and a supercuspidal representation $(\sigma, W)$ of $M(F)$ such that $(\pi, V)$ is a subrepresentation of $(\Ind_{P(F)}^{G(F)} \sigma, \Ind_{P(F)}^{G(F)} W)$.
\end{theorem}

So, how can we construct supercuspidal representations?
One way to do (at least, one way to construct \emph{a} representation in an interesting way) is to use induction from a compact subgroup.
For example, consider the following diagram:

\begin{center}
\begin{tikzcd}
    \GL_2(\bQ_p) & \\
    \GL_2(\bZ_p) \arrow[u, hookrightarrow] \arrow[r, twoheadrightarrow] & \GL_2(\bF_p)
\end{tikzcd}
\end{center}
Let's assume that representations of finite groups are ``easier'' to understand.\footnote{Maybe not... but at least for small $p$'s, you can compute them by hand. In general, you may need Deligne--Lusztig theory.}
Once we have an irreducible representation $\rho$ of $\GL_2(\bF_p)$ (which is a finite group), we can pullback it to $\GL_2(\bZ_p)$ and then induce it to $\GL_2(\bQ_p)$.
Then we may prey that the induced representation is irreducible, or even supercuspidal.
This works sometimes - for example, if $\rho$ is a \emph{Weil representation} of $\GL_2(\bF_p)$, then the pullbacked \& induced representation is supercuspidal (you may find details in \cite[Chapter 4]{bump1998automorphic}).
Howe \cite{howe1977tamely} give a construction of a lot of supercuspidal representations of $\GL_n(F)$, which turned out to be exhaustive by Moy \cite{moy1986local}.


It is a folklore conjecture that all supercuspidal representations (of general reductive groups) arise via compact induction from a representation of a compact-mod-center open subgroup.
Although we don't know how to prove the conjecture yet, most of the known constructions of the supercuspidal representations would be based on the idea.
Hence it is important to know what compact-mod-center subgroups we need to consider and what representations of them we need to induce.
The naive answer that we'll see is the following:

\bigskip
\begin{myquote}
For each $G$, there exists a contractible complete metric space $\scB(G)$ called \emph{Bruhat--Tits building} where $G(\bQ_p)$ acts nicely. Each point $x \in \scB(G)$ gives a \emph{Moy--Prasad filtration} $\{G_{x, r}\}_{r \in \bR_{\ge 0}}$, compact open subgroups of the stabilizer subgroup $G_{x} \subset G$, whose quotients are Lie groups of finite type or abelian groups.
Yu's construction produces a supercuspidal representation to \emph{Yu's datum}, which consists of (i) a finite filtration $G$, (ii) a vertex in $\scB(G)$, (iii) depth-zero cuspidal representation of the smallest subgroup in the filtration, and (iv) \emph{generic} characters of the filtration subgroups.
\end{myquote}

% \newpage

% The following lemma tells you that irreducibility is enough to guarantee supercuspidality.

% \begin{lemma}
% \label{lem:cind}
% Let $K$ be a compact-mod-center open subgroup of $G(F)$ and let $\rho$ be an irreducible representation of $K$.
% If the compact induction $\cInd_K^{G(F)} \rho$ is irreducible, then is supercuspidal.
% \end{lemma}
