\newpage
\section{Principal $G$-bundles and topologies (September 20)}

Let $G$ be a reductive group over $\mathbb{C}$, and let $\mathcal{P}$ be a principal
$G$-bundle on a curve $X$ over $\mathbb{C}$ (which is also a $G$-torsor on $X$).
Tannaka's theorem tells us that we can reconstruct $G$ from its category of representations $\mathsf{Rep}_{G}$
which is naturally a tensor category (for given two representations of $G$, we have a tensor product representation of them).
Using this, we can prove that there's a natural bijection between 
\begin{align*}
    \boxed{
        \text{principal $G$-bundles on $X$ (w.r.t. particular topology) with connection}
    }
\end{align*}
and
\begin{align*}
    \boxed{
        \text{Tensor functors $\mathsf{Rep}_{G}(\mathbb{C}) \to \mathsf{VecBun}^{\nabla}(X)$ (w.r.t. same topology)}
    }
\end{align*}
where the map is given by
$$
(\mathcal{P}, \nabla) \mapsto \mathcal{F}_{\mathcal{P}}: (\rho, V) \mapsto \mathcal{P} \times V
$$
where $\mathcal{P}$ acts on $V$ via $\rho$.
Note that tensor product on the category $\mathsf{VecBun}^{\nabla}$ (vector bundle with connection) is defined as
$$
(V, \nabla_V) \otimes (W, \nabla_W) := (V \otimes W, \nabla_V \otimes \mathrm{id}_W + \mathrm{id}_V \otimes \nabla_W).
$$

Last week, we gave a correspondence between (flat) holomorphic/algebraic $\hat{G}$-bundles on $X$ with 
a double coset space $G(F)\backslash G(\mathbb{A}_F) / G(\mathcal{O}_F)$, for everywhere-unramified cases.
What if we allow ramifications? What kind of geometric objects would correspond to the flat $\hat{G}$-bundles?
Before we give an answer, we need to specify what kind of topology are we going to impose on $X$.

In algebraic geometry, there's a versatile notion of \emph{Grothendieck topology}
in which open set $U\subset X$ is replaced by morphisms $U \to X$ of certain type.\footnote{To be more precise, Grothendieck topology is a topology
on a certain category of morphisms associated to $X$}
For example, Grothendieck topology defined with \'etale morphisms $U \to X$ is called \emph{\'etale topology}.
We have the following inclusion of topologies: $A \rightarrow B$ means that $B$ is finer than $A$.\footnote{fppf: flat and locally of finite presentation, fpqc: faithfully-flat and quasi-compact.}
\begin{align*}
    \boxed{
        \text{Zariski $\rightarrow$ \'etale $\rightarrow$ fppf $\rightarrow$ fpqc}
    }
\end{align*}
With Grothendieck topology on $X$, principal $G$-bundle is a scheme $\mathcal{P}$ with $G$-equivariant morphism $\pi: \mathcal{P} \to X$
such that 1) it is locally trivial in the sense that we have a covering of $X$ with (certain type of) morphisms
$\{\iota_{\alpha}:U_{\alpha} \to X\}_{\alpha}$ such that pullback of $\mathcal{P}$ to $U_\alpha$, $\iota_{\alpha}^{*}\mathcal{P}=\mathcal{P}\times_{X} U_{\alpha}$, is 
isomorphic to $G \times U_{\alpha}$ (i.e. trivial), and 2) the morphism $\iota_{\alpha}$ ``agree on intersections'' in the sense that pullback of $\mathcal{P}$
along two morphisms
\begin{align*}
U_{\alpha} \times_X U_{\beta} \xrightarrow{\iota_{\alpha\beta}} U_{\alpha} \xrightarrow{i_{\alpha}} X \\
U_{\alpha} \times_X U_{\beta} \xrightarrow{\iota_{\beta\alpha}} U_{\beta} \xrightarrow{i_{\alpha}} X
\end{align*}
are isomorphic.

Notion of a principal $G$-bundle depends on the topology.
For example, consider a double covering 

\begin{center}
    \begin{tikzcd}
        Y = \mathrm{Spec}\mathbb{C}[y, y^{-1}] \simeq \mathbb{A}^{1} \backslash \{0\}\arrow[d]  \\
        X = \mathrm{Spec}\mathbb{C}[x, x^{-1}] \simeq \mathbb{A}^{1} \backslash \{0\}
    \end{tikzcd}
\end{center}
corresponds to a map $\mathbb{C}[x, x^{-1}] \to \mathbb{C}[y, y^{-1}], x \mapsto y^2$.
We have a $\mathbb{Z}/2$-action on $Y$ given by $y \mapsto -y$.
With \'etale topology, this automorphic imposes a $\mathbb{Z}/2$-bundle structure on $Y\to X$.
However, this can't be a $\mathbb{Z}/2$-bundle with Zariski topology.
In fact, any open subset of $X$ in Zariski topology has a form of $X \backslash S$ for some finite set $S \subset X$, 
and there's no $U\subset X$ such that $Y|_{U} \simeq U \coprod U$ (i.e. it can't be locally trivial).

There are some \emph{special} groups $G$ where local triviality of principal $G$-bundle on Zariski topology is equivalent to
that on \'etale topology, such as $G = \GL_n, \SL_n, \mathrm{Sp}_n$.
For such groups, it is also true that local triviality with Zariski topology is also equivalent to that on fpqc topology.

In case of $\GL_n$, we have the following 1-1 correspondences:
\begin{center}
    \begin{tikzcd}
        \boxed{\text{Locally free sheaves of } \mathcal{O}_X\text{-mod of rank }n } \arrow[d, leftrightarrow] \\
        \boxed{\text{Vector bundles of rank }n} \arrow[d, leftrightarrow]\\
        \boxed{\text{Principal }\GL_n\text{-bundles}}
    \end{tikzcd}
\end{center}
this follows from Grothendieck's faithful flat descent.
Grothendieck also proved that the notion of $G$-bundle coincides on fpqc and \'etale topology
when $G$ is a reductive group.
When $X$ is a projective curve over an algebraically closed field, the notion of $G$-bundle with \'etale, Zariski, and analytic topology all coincides, and this implies that
we have a bijection
\begin{center}
    \begin{tikzcd}
        \boxed{G(F) \backslash G(\mathbb{A}_F) / G(\mathcal{O}_F)} \arrow[d, leftrightarrow] \\
        \boxed{\text{equivalence classes of principal }G\text{-bundles loc. triv. in Zariski topology}}
    \end{tikzcd}
\end{center}
which is due to Drinfeld-Simpson.



