\newpage
\section{Enhanced Fourier-Mukai transform (October 18)}

We'll explain about enhanced Fourier-Mukai transform in detail.
For an abelian variety $A$ over $\mathbb{C}$, the original Fourier-Mukai transform is between 
bounded derived category of coherent sheaves of $\mathcal{O}_A$-modules and that of $\mathcal{O}_{A^\vee}$-modules.
It is defined in a same way as before (using Poincare bundle, pullback, and pushforward).
For a line bundle $L$ on $A$, a sheaf of sections of $L$ (which is a coherent $\mathcal{O}_A$-module)
sends to the skyscraper sheaf $\mathcal{O}_L$ supported at $L \in A^\vee$, that is a coherent
$\mathcal{O}_{A^\vee}$-module.

For \emph{enhanced} version of Fouier-Mukai transform, we need to define $A^\natural$ first.
It is a moduli space of line bundles on $A$ with flat connection. 
For such a bundle $(L, \nabla)$, degree of $L$ is always zero.
Then one has (enhanced) Poincare bunde $\mathcal{P}$ on $A^\natural \times A$
defined by the universal property of $A^\natural$ (the bundle corresponds to the identity map in $\mathrm{Hom}(A^\natural, A^\natural)$).
For the below diagram
\begin{center}
    \begin{tikzcd}
        & \mathcal{P} \arrow[d] & \\
        & A^\natural \times A \arrow[dl, "p_1", swap] \arrow[dr, "p_2"] & \\
        A^\natural & & A
    \end{tikzcd}
\end{center}
we can define functors between the bounded derived category of coherent $\mathcal{O}_{A^\natural}$-modules and  
that of $D$-modules on $A$.
We obtain geometric Langlands for $\GL_1$ when $A = \Jac_X$.

As we did for $\Loc_{\GL_1}(X)$, we have a map $A^\natural \to A^\vee$ defined by $(L, \nabla)$, 
and the fiber of the map is the space of all flat connections on $L$, which is a torsor over $\rH^0(A, \Omega_A^{1, 0})$.
In other words, $A^\natural$ is an affine bundle on $A^\vee$ modeled on $\rH^0(A, \Omega_A^{1, 0}) = T_{0}^*A$.
When $A = V /\Lambda$ for $g$-dimensional complex vector space $V \simeq \mathbb{C}^g$ and a lattice
$\Lambda$ (rank $2g$ free $\mathbb{Z}$-module) in $V$, we can express $A^\vee$ and $A^\natural$ as follows.

\begin{theorem}[Arinkin]
Let $A = V / \Lambda$ be an abelian variety of dimension $g$.
\begin{enumerate}
    \item $A^\vee \simeq \overline{V}^{*} / \Lambda^{*}$, where $\Lambda^{*}$ is a dual lattice of $\Lambda$ in $\overline{V}^{*}$.
    \item $A^\natural \simeq (\overline{V}^{*} \oplus V) / \Lambda^{*}_{\mathrm{diag}}$, where $\Lambda^{*}_{\mathrm{diag}}$ is a diagonal lattice
    defined as an image of $\Lambda^{*} \hookrightarrow \overline{V}^{*} \oplus V^{*}$
    \item The natural extension 
    \begin{center}
        \begin{tikzcd}
            0 \arrow[r] & V^{*} \arrow[r] \arrow[d, "\simeq"] & (\overline{V}^{*} \oplus V^{*}) / \Lambda_{\mathrm{diag}}^{*} \arrow[r] \arrow[d, "\simeq"] & \overline{V}^{*} / \Lambda^{*} \arrow[r] \arrow[d, "\simeq"] & 0 \\
            0 \arrow[r] & \rH^{0}(A, \Omega_{A}^{1, 0}) \arrow[r] & A^{\natural} \arrow[r] & A^{\vee} \arrow[r] & 0
        \end{tikzcd}
    \end{center}
    is a universal extension.
\end{enumerate}
\end{theorem}
Note that when $A = V /\Lambda$, $V \simeq T_{0}A$ and $V^{*} \simeq \rH^{0}(A, \Omega^{1,0})$ and $\overline{V}^{*} \simeq \rH^{0}(A, \Omega^{0,1}) \simeq \rH^{1}(A, \mathcal{O}_A)$
and $\Lambda^{*} \simeq \rH_1(A, \mathbb{Z})^{*} \simeq \rH^{1}(A, \mathbb{Z})$ by Poincare duality.
This is compatible with $A^\vee \simeq \rH^{1}(A, \mathcal{O}_A) / \rH^{1}(A, \mathbb{Z})$ obtained by cohomology sequence
induced from $0 \to \mathbb{Z} \to \mathcal{O}_A \to \mathcal{O}_A^{\times} \to 0$.

